---
title: "REAMDE"
author: "Ondrej Mottl"
date: "26/05/2021"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>")
```

# Rate-of change analyses in paleoecological sequences and the new R-Ratepol package
Materials for Seminar Day of PalaeoSIG: Data Manipulation & Statistical Analysis in Palaeoecology 

See the slides at http://bit.ly/R-ratepol-workshop-slides

Preprint about R-Ratepol package: http://bit.ly/R-Ratepol-preprint

GitHub with R-Ratepol: https://bit.ly/R-Ratepol-package

## Seminar day

### Instal packages
```{r install_packages, eval=FALSE}
# run this script before the seminar
source("R/00_Install_packages.R")
```

### Script description

R/00_Config_file.R:
 
 - configuration script for the repo

R/01_Example_01.R:
 
 - Workflow showing full strength of *RRatepol package* and serve as 
 step by step guidance starting from downloading dataset from Neotoma,
 building age-depth models, to estimating rate-of-change 
 using age uncertainty. 

R/02_Example_02.R:

 - Script showing various setting in estimation of RoC. 
